Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-16 csf-2017/paper.tex
Small textual change.

\begin{lemma}
  \label{lem:correctness-g1}
  Let
\[
    \begin{array}{r@{}lr@{}l}
    c_{\var{adv}} & \;\defeq ((\rwx,\glob),\dots) & c_{g1} & \;\defeq ((\entry,\glob),\dots)
    \end{array}
\]
  and otherwise make assumptions about capabilities and linking similar to Lemma~\ref{lem:correctness-f1} 
  if
  \[
  (\reg_0\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},m) \step^* (\halted,m'),
  \]
  then $m'(\flag) = 0$.
\end{lemma}

As explained in Section~\ref{sec:stack-and-return-pointer}, the callback must be
global, essentially to make sure that it is not allocated on the stack where it
might contain the adversary's original stack pointer. If not, it could break the
encapsulation of our local stack frame. In the proof of
Lemma~\ref{lem:correctness-g1}, this requirement shows up because we invoke the
callback in a world that is only a private future world of the one where we
received the callback, precisely because we have invalidated the local state of
the adversary (particularly its previous stack and return capabilities). The
callback is still valid in this private future world, but only because we know
that it is global.

>>>>

\begin{lemma}
  \label{lem:correctness-g1}
  Let
\[
    \begin{array}{r@{}lr@{}l}
    c_{\var{adv}} & \;\defeq ((\rwx,\glob),\dots) & c_{g1} & \;\defeq ((\entry,\glob),\dots)
    \end{array}
\]
  and otherwise make assumptions about capabilities and linking similar to Lemma~\ref{lem:correctness-f1}.
  Then if
  \[
  (\reg_0\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},m) \step^* (\halted,m'),
  \]
  then $m'(\flag) = 0$.
\end{lemma}

As explained in Section~\ref{sec:stack-and-return-pointer}, the
macro-instruction \texttt{\footnotesize{reqglob $r_1$}} checks that the callback
is global, essentially to make sure it is not allocated on the stack where it
might contain old stack pointers or return pointers. If not, it could break the
encapsulation of our local stack frame. In the proof of
Lemma~\ref{lem:correctness-g1}, this requirement shows up because we invoke the
callback in a world that is only a private future world of the one where we
received the callback, precisely because we have invalidated the local state of
the adversary (particularly its previous stack and return capabilities). The
callback is still valid in this private future world, but only because we know
that it is global.
